---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# dropR: An R Package for Dropout Analysis

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of dropR from
[GitHub](https://github.com/iscience-kn/dropR) with:

``` r
# install.packages("remotes")
remotes::install_github("iscience-kn/dropR")
```

We are currently working to get `dropR` back on CRAN. 
Once it’s up again, you can install dropR via

``` r
install.packages("dropR")
```

## Usage as a Shiny App (Graphical User Interface)

To start `dropR's` built-in GUI, run

```{r eval = F}
dropR::start_app()
```

or visit the [dropR Web App](https://iscience-kn.shinyapps.io/dropR/)

## Interactive Usage (use dropR on the R Console)

You can also use dropR’s functionality within R, i.e., either in the
console or within your own functions and packages.
Read more about interactive usage of dropR in our [walkthrough article](articles/interactive.html).

![Fig. 1: dropR Example Plot from `plot_do_curve()`.](./man/figures/dropR_1717579088.svg)


<!-- # ```{r do_plot_ex, echo = F} -->
<!-- # library(dropR) -->
<!-- # df <- add_dropout_idx(dropRdemo, 3:54) -->
<!-- # stats <- compute_stats(df, -->
<!-- #                        by_cond = "experimental_condition", -->
<!-- #                        no_of_vars = 52) -->
<!-- # plot_do_curve(stats, full_scale = F) + ggplot2::labs(title = "Dropout by condition") -->
<!-- # ``` -->
