---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dropR: An R Package for Dropout Analysis

<!-- badges: start -->
<!-- badges: end -->


## Installation

You can install the development version of dropR from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("iscience-kn/dropR")
```


We are currently working to get `dropR` back on CRAN. Once it's up again, you can
install dropR via 

```{r, eval=FALSE}
install.packages("dropR")
```


## Usage as a Shiny App (Graphical User Interface)

To start `dropR's` built-in GUI, run

```{r,eval=FALSE}
dropR::start_app()
```

## Interactive Usage (use dropR on the R Console)

You can also use dropR's functionality within R, i.e., either on the console or within your
own functions and packages. Read more about interactive usage of dropR in our [walkthrough article](articles/interactive.html).



```{r, echo=FALSE}
library(dropR)
data("dropRdemo")

qs <- which(grepl("vi_", names(dropRdemo)))
# add numeric drop out position to original dataset
dropRdemo <- add_dropout_idx(dropRdemo, q_pos = qs)

stats_table <- compute_stats(dropRdemo,
                             by_cond = "experimental_condition",
                             no_of_vars = length(qs))


```

```{r, echo=FALSE}
plot_do_curve(stats_table)
```


