---
title: "R Console Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{r_console_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(dropR)
```

Though the low-hurdle of the online version with its graphical user interface (GUI)
is appealing for many use cases, there are good reasons to directly use dropR's backend on the R console - without the GUI: Some data.frames may need extra formatting or additional cleaning before they suit the dropR input format or you may want adapt and extend your analysis in a way the GUI does not allow to. 


## Dropout Analysis Walkthrough

This section describes how to extract information on dropout from the demo dataset without using the dropR shiny UI. First, let's make sure the dema dataset is 
loaded and available. They dataset should look like this

```{r}
library(dropR)
data("dropRdemo")
```


### Basic Dropout Statistics

Now, let's extract dropout, i.e., information on when participant dropped out of the questionnaire and never returned. In the demo dataset questions are easily identified by their prefix `vi_`

```{r}
qs <- which(grepl("vi_", names(dropRdemo)))
# add numeric drop out position to original dataset
dropRdemo <- add_dropout_idx(dropRdemo,q_pos = qs)
head(dropRdemo[,c(1:3,53,54)])
```

The `experimental_condition` column indicates belonging to a sub sample group each of which was treated differently. For example, groups receive a different sequence of questions or different wording. Now, let's compute a table containing basic dropout statistics for each item.



```{r}
library(kableExtra)
stats_table <- compute_stats(dropRdemo,
                             by_cond = "experimental_condition",
                             no_of_vars = length(qs))
kable(head(stats_table))
```

Out of `r {nrow(dropRdemo)}` participants in the demo sample, `r stats_table$remain[1]` participants remain in the survey, accounting for `r round(stats_table$pct_remain[1]* 100,digits=2)` percent of the sample.
The `cs` column shows the cummulative dropout count.


### Plotting Dropout Curves

Based on the above statistics table, dropR plots dropout curves very conveniently.

```{r}
plot_do_curve(stats_table)

```




