---
title: "Running DropOut related Tests Within R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running DropOut related Tests Within R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(dropR)
data("dropRdemo")
qs <- which(grepl("vi_", names(dropRdemo)))
dropRdemo <- add_dropout_idx(dropRdemo, q_pos = qs)

stats_table <- compute_stats(dropRdemo,
                             by_cond = "experimental_condition",
                             no_of_vars = length(qs))

# add numeric drop out position to original dataset


```

### Running a Chi-sq. Test for a Selected Question

> **_NOTE:_**  Chi-sq. tests are only available when an column denoting the experimental condition is given.

Let's compute a Chisq test at question 15 for experimentatl conditions `11` and `12`, dropR's dropout Chisq-Test returns a list containing the actual *test results* and dropout overview table at the selected question. 


```{r}
do_chisq(stats_table,
         chisq_question = 15,
         sel_cond_chisq = c('11','12'),
         p_sim = TRUE)
```

### Kaplan-Meier Estimation

```{r}
kpm <- do_kpm(d = add_dropout_idx(dropRdemo, 3:54),
              condition_col = "experimental_condition",
              model_fit = "total")

head(kpm$steps)

head(kpm$d)

kpm$model_fit




```






